Results visualization across sites

### 2021-11-17 metanalysis_visualization/visualization.Rmd
added visualization for total number of patients per site per month

>>>>

### Total number of patients per month an site

```{r}
patients_hospitalized_agg_sex_perc_all %>%
  select( time_p, count, siteid) %>%
  unique() %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date) %>%
  ggplot(aes(x = time_p, y = count, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "number of patients",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Total number of patients with mental disorders per site \n ( per ", time_period,")"))
```
```
